---
title: Saldae Analytics Daily report
author: Faridh
date: 2021-03-03 11:36
output:
  html_document:
    toc: yes
    mathjax: ~
    toc_float: yes
params:
  sald_explor_chart: NA
  sald_predict_chart: NA
  sald_predict_values: NA
  sald_predict_comment: NA
  sald_introduction: NA
  sald_report_asezwer: NA
---
# Saldae {data-navmenu="Intro"}

<!-- Row {data-width=200} -->
<!-- ----------------------------------------------------------------------- -->
<!-- ### Analysis Summary {data-commentary-height=200} -->

<!-- ```{r,echo=FALSE,warning=FALSE,results='asis'} -->

<!-- h4(params$sald_report_asezwer) -->
<!-- ``` -->

<!-- *** -->

```{r,echo=FALSE,warning=FALSE}
aa <<- params
future_key_figures <- unlist(params$sald_predict_values$key_figures%>%purrr::map(~.x[[1]]))
future_key_figures <- data.frame(attribute = names(future_key_figures),forecast =future_key_figures)


```

Row {data-width=500}
-----------------------------------------------------------------------
### Key Figures ( Prediction)
```{r,echo=FALSE,warning=FALSE}


DT::datatable(future_key_figures,
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```


### Key figures (contribution)
```{r,echo=FALSE,warning=FALSE}
future_key_figures_pie <- future_key_figures%>%plotly::plot_ly( labels  = ~attribute, values= ~forecast, type = 'pie')

future_key_figures_pie
```



Row
-----------------------------------------------------------------------
### Intro {data-commentary-height=400}

This is a template of interactive reporting output generated by [Saldae Analytics Platform](https://saldae-analytics.shinyapps.io/saldae-analytics-platform/).
If you want to learn more about us and our service please visit our website: 

[https://www.saldaeanalytics.com/](https://www.saldaeanalytics.com/)

*Total Sales of Beers in the following cities next month :* 

```{r,echo=FALSE,warning=FALSE}
future_key_figures_bar <- future_key_figures%>%plotly::plot_ly( y = ~attribute, x = ~forecast, type = 'bar',color = ~attribute, orientation = 'h')
future_key_figures_bar

```


***

### Useful concepts {data-commentary-height=300}


**Forecasting:**

Forecasting is required in many situations. Stocking an inventory may require forecasts of demand months in advance. Telecommunication routing requires traffic forecasts a few minutes ahead. Whatever the circumstances or time horizons involved, forecasting is an important aid in effective and efficient planning

***


## `r names(params$sald_explor_chart)[[1]]` {.tabset}



### Sales Forecast

```{r, warning=FALSE,echo=FALSE}
params$sald_explor_chart[[1]]

```


### Sales by State

```{r, warning=FALSE,echo=FALSE}

DT::datatable(params$sald_predict_chart[[1]],
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
# reactable::reactable(params$sald_predict_chart[[1]],pagination = FALSE, highlight = TRUE, height = 200)

```



### Sales by Category 

```{r, warning=FALSE,echo=FALSE}
# reactable::reactable(params$sald_predict_chart[[1]],pagination = FALSE, highlight = TRUE, height = 400)
DT::datatable(params$sald_predict_chart[[1]],
              extensions = 'Scroller', options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE
  )
)

```

### Best Sellers

aru-d kra dagia ghas dirit

## `r names(params$sald_explor_chart)[[2]]` {.tabset}



### Sales Forecast

```{r, warning=FALSE,echo=FALSE}
params$sald_explor_chart[[2]]

```


### Sales by State

```{r, warning=FALSE,echo=FALSE}

DT::datatable(params$sald_predict_chart[[2]],
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
# reactable::reactable(params$sald_predict_chart[[2]],pagination = FALSE, highlight = TRUE, height = 200)

```



### Sales by Category 

```{r, warning=FALSE,echo=FALSE}
# reactable::reactable(params$sald_predict_chart[[2]],pagination = FALSE, highlight = TRUE, height = 400)
DT::datatable(params$sald_predict_chart[[2]],
              extensions = 'Scroller', options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE
  )
)

```

### Best Sellers

aru-d kra dagia ghas dirit

## `r names(params$sald_explor_chart)[[3]]` {.tabset}



### Sales Forecast

```{r, warning=FALSE,echo=FALSE}
params$sald_explor_chart[[3]]

```


### Sales by State

```{r, warning=FALSE,echo=FALSE}

DT::datatable(params$sald_predict_chart[[3]],
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
# reactable::reactable(params$sald_predict_chart[[3]],pagination = FALSE, highlight = TRUE, height = 200)

```



### Sales by Category 

```{r, warning=FALSE,echo=FALSE}
# reactable::reactable(params$sald_predict_chart[[3]],pagination = FALSE, highlight = TRUE, height = 400)
DT::datatable(params$sald_predict_chart[[3]],
              extensions = 'Scroller', options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE
  )
)

```

### Best Sellers

aru-d kra dagia ghas dirit

## `r names(params$sald_explor_chart)[[4]]` {.tabset}



### Sales Forecast

```{r, warning=FALSE,echo=FALSE}
params$sald_explor_chart[[4]]

```


### Sales by State

```{r, warning=FALSE,echo=FALSE}

DT::datatable(params$sald_predict_chart[[4]],
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
# reactable::reactable(params$sald_predict_chart[[4]],pagination = FALSE, highlight = TRUE, height = 200)

```



### Sales by Category 

```{r, warning=FALSE,echo=FALSE}
# reactable::reactable(params$sald_predict_chart[[4]],pagination = FALSE, highlight = TRUE, height = 400)
DT::datatable(params$sald_predict_chart[[4]],
              extensions = 'Scroller', options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE
  )
)

```

### Best Sellers

aru-d kra dagia ghas dirit

## `r names(params$sald_explor_chart)[[5]]` {.tabset}



### Sales Forecast

```{r, warning=FALSE,echo=FALSE}
params$sald_explor_chart[[5]]

```


### Sales by State

```{r, warning=FALSE,echo=FALSE}

DT::datatable(params$sald_predict_chart[[5]],
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
# reactable::reactable(params$sald_predict_chart[[5]],pagination = FALSE, highlight = TRUE, height = 200)

```



### Sales by Category 

```{r, warning=FALSE,echo=FALSE}
# reactable::reactable(params$sald_predict_chart[[5]],pagination = FALSE, highlight = TRUE, height = 400)
DT::datatable(params$sald_predict_chart[[5]],
              extensions = 'Scroller', options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE
  )
)

```

### Best Sellers

aru-d kra dagia ghas dirit

## `r names(params$sald_explor_chart)[[6]]` {.tabset}



### Sales Forecast

```{r, warning=FALSE,echo=FALSE}
params$sald_explor_chart[[6]]

```


### Sales by State

```{r, warning=FALSE,echo=FALSE}

DT::datatable(params$sald_predict_chart[[6]],
              extensions = c('Buttons','Scroller'), options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE,
              dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
# reactable::reactable(params$sald_predict_chart[[6]],pagination = FALSE, highlight = TRUE, height = 200)

```



### Sales by Category 

```{r, warning=FALSE,echo=FALSE}
# reactable::reactable(params$sald_predict_chart[[6]],pagination = FALSE, highlight = TRUE, height = 400)
DT::datatable(params$sald_predict_chart[[6]],
              extensions = 'Scroller', options = list(
                deferRender = TRUE,
              scrollY = 200,
              scroller = TRUE
  )
)

```

### Best Sellers

aru-d kra dagia ghas dirit
